---
title: "current meter temperature calibrations"
author: "Ben Cresswell"
date: today
date-format: "DD/MM/YYYY"
format: 
  html:
    ## Format
    theme: spacelab
    html-math-method: mathjax
    ## Table of contents
    toc: true
    toc-float: true
    ## Numbering
    number-sections: true
    number-depth: 3
    ## Layout
    fig-caption-location: "bottom"
    fig-align: "center"
    fig-width: 4.8
    fig-height: 3
    fig-dpi: 100
    tbl-cap-location: top
    ## Code
    code-fold: false
    code-tools: true
    code-summary: "Show the code"
    code-line-numbers: true
    code-block-border-left: "#ccc"
    highlight-style: zenburn
    ## Execution
    execute:
      echo: true
      cache: true
    ## Rendering
    embed-resources: true
documentclass: article
fontsize: 12pt
execute-dir: project
mainfont: Arial
classoption: a4paper
---

# Introduction
This document calculates calibrations/offsets for temperature probes in MNI CMs. Temp readings are calibrated from a pool test where CMs were tested against a HOBO MX Light/Temp logger 

## Set up and housekeeping
```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(cache.lazy = FALSE,
                      tidy = "styler")
options(tinytex.engine = "xelatex")
rm(list=ls())
```


```{r}
library(readxl)
library(tidyverse)
```


# Load current meter csv files 
```{r}
cm_filelist = list.files(path = "data/temperature_cal",
               pattern = ".csv",
               full.names = TRUE)

cm_temp_raw <- purrr::map_df(cm_filelist, read.csv, stringsAsFactors = TRUE, .id = 'filename')  |> 
  dplyr::mutate(CM_id = as_factor(paste0("M", str_pad(filename, width = 4, side = "left", pad = "0"))), .keep = "unused")
```


```{r}

cm_temp_sum <- 
  cm_temp_raw |> 
  mutate(datetime = lubridate::as_datetime(datetime)) |> 
  #mutate(date = lubridate::as_date(datetime)) |> 
  mutate(hour = hour(datetime)) |> 
  mutate(minute = str_pad(minute(datetime), width = 2, side = "left", pad = "0")) |> 
  mutate(time = paste(hour, minute, sep = ":")) |> 
  filter(time > "16:49" &
           time < "17:10")  |> 
  group_by(CM_id) |> 
  summarise(mean_temp = mean(temp..Celsius.))
```

M8 and 9 are too far out to use temp data.


# Std dev (with outliers excluded)
```{r}
cm_temp_sum |> 
  filter(mean_temp > 30 &
           mean_temp < 31) |> 
  summarise(sd = sd(mean_temp))
```


# Load hobo data and calculate mean for same period
```{r}
hobo <- read_excel("data/hobo_ref_file.xlsx") |> 
  rename(datetime = `Date-Time (AST)`) |> 
   mutate(hour = hour(datetime)) |> 
   mutate(minute = str_pad(minute(datetime), width = 2, side = "left", pad = "0")) |> 
   mutate(time = paste(hour, minute, sep = ":")) |> 
   filter(time > "16:49" &
           time < "17:10") |> 
    summarise(mean_temp = mean(`Temperature (°C)`))

```




